Reliable Inferences from Simply Parameterised Models

### 2013-08-27 SandBox/ms.tex
Z

One distribution for $\theta$ that we can compute is the following:
\begin{eqnarray}
q_\eta(\theta | x) \propto p_s(\theta)\mathcal{L}_\eta(\theta; x).
\end{eqnarray}
Here $\mathcal{L}$ is some scalar that quantifies the match between $\theta$ and
$x$ and it also depends on adjustable parameter(s) $\eta$. A concrete example
would be saying that $\mathcal{L}_\eta(\theta; x) = p_s(x|\theta)^{1/\eta}$, i.e.
using a tempered version of the simple model's likelihood function.
The expected score (with a logarithmic scoring rule) when using this approximating
distribution is
\begin{eqnarray}
\int p_c(\theta | x) \log q_\eta(\theta | x) \, d\theta
\end{eqnarray}
and we want to choose the value of $\eta$ that maximises this.

Alright, I'll now bite the bullet. Optimising the expected score, given the data,
is hard. What if we optimise the pre-data expected score? This is
\begin{eqnarray}
\iint p_c(x) p_c(\theta | x) \log q_\eta(\theta | x) \, d\theta \, dx
\end{eqnarray}

>>>>

One distribution for $\theta$ that we can compute is the following:
\begin{eqnarray}
q_\eta(\theta | x) \propto p_s(\theta)\mathcal{L}_\eta(\theta; x).
\end{eqnarray}
The normalised version of this distribution is
\begin{eqnarray}
q_\eta(\theta | x) &=& \frac{p_s(\theta)\mathcal{L}_\eta(\theta; x)}
{\mathcal{Z}(\eta; x)}
\end{eqnarray}
where $\mathcal{Z}(\eta; x) = \int p_s(\theta)\mathcal{L}_\eta(\theta; x) \, d\theta$.

Here $\mathcal{L}$ is some scalar that quantifies the match between $\theta$ and
$x$ and it also depends on adjustable parameter(s) $\eta$. A concrete example
would be saying that $\mathcal{L}_\eta(\theta; x) = p_s(x|\theta)^{1/\eta}$, i.e.
using a tempered version of the simple model's likelihood function.
The expected score (with a logarithmic scoring rule) when using this approximating
distribution is
\begin{eqnarray}
\int p_c(\theta | x) \log q_\eta(\theta | x) \, d\theta\\
&=& \int q_\eta(\theta | x) \frac{p_c(\theta | x)}{q_\eta(\theta | x)} \log q_\eta(\theta | x) \, d\theta
\end{eqnarray}
and we want to choose the value of $\eta$ that maximises this.

%We could do a MaxEnt type approximation, which IMO is not correct here because
%the constraint is only an approximation and not legitimate information. But it
%might be tractable.
